Modelling results

### 2024-09-04 notebooks/02-modelling-results.qmd
Correlations, congruence models, rank transforms

@@

ggsave(here("figures/checks-implicit.png"), dpi = 600)
```

@@

ggsave(here("figures/checks-explicit.png"), dpi = 600)
```

>>>>

## Group differences

### Table

::: {#supptbl-questionnaire-results}
```{r}
group_effects <- 
  df_questionnaires |>
  pivot_longer(
    cols = c("Implicit effect":"SUIS"),
    names_to = "questionnaire",
    values_to = "score"
  ) |> 
  group_by(questionnaire) |> 
  nest() |> 
  rowwise() |> 
  mutate(
    lm = list(
      lm(score ~ aphantasia, data = data)
    ),
    lm_ranked = list(
      lm(rank(score) ~ aphantasia, data = data)
    ),
    ranked_means = list(
      prepare_means(lm_ranked, questionnaire)
    ),
    table = list(
      generate_model_summary(lm, lm_ranked, questionnaire)
    )
  )

bind_rows(group_effects$table) |> display()
```
:::

### Plot

```{r}
# dodge width for all the geoms
dw <- 1
# axis text size
txt <- 14
# legend text size
txt_legend <- 12

norm_means <- 
  df_q_norm |> 
  group_by(aphantasia) |>
  reframe(across(VVIQ:SUIS, mean)) |> 
  pivot_longer(
    cols = c(VVIQ:SUIS),
    names_to = "Questionnaire",
    values_to = "Mean"
  ) |>
  mutate(
    Questionnaire = fct_relevel(
      Questionnaire, 
      c("VVIQ", "SUIS", "OSIQ_Object", "OSIQ_Spatial")
    ))

df_q_norm |> 
  pivot_longer(
    cols = c(VVIQ:SUIS),
    names_to = "Questionnaire",
    values_to = "Score"
  ) |>
  mutate(
    Questionnaire = fct_relevel(
      Questionnaire, 
      c("VVIQ", "SUIS", "OSIQ_Object", "OSIQ_Spatial")
    )) |> 
  ggplot(aes(
    x = Questionnaire, 
    y = Score, 
    fill = aphantasia, 
    color = aphantasia
    )) +
  # accentuation of the median line at 0.5
  geom_hline(
    yintercept = .5,
    linetype = 1,
    color = "grey30",
    alpha = .2
  ) +
  # violin shapes for the distributions and quantiles
  geom_violin(
    position = position_dodge(dw),
    alpha = .1,
    draw_quantiles = c(.25, .5, .75)
  ) +
  # points for means and lines for CIs
  geom_point(
    data = norm_means,
    aes(
      x = Questionnaire,
      y = Mean,
      color = aphantasia
    ),
    size = 2,
    position = position_dodge(dw)
  ) +
  # star for significance
  annotate(
    geom  = "text",
    label = "*",
    color = "black",
    x = 1,
    y = .95,
    size  = 10 
    ) +
  # dotted line that separates the different questionnaires
  geom_vline(
    aes(xintercept = stage(Questionnaire, after_scale = 1.5)),
    linetype = 3
  ) +
  # star for significance
  annotate(
    geom  = "text",
    label = "*",
    color = "black",
    x = 2,
    y = .95,
    size  = 10 
    ) +
  # dotted line that separates the different questionnaires
  geom_vline(
    aes(xintercept = stage(Questionnaire, after_scale = 2.5)),
    linetype = 3
  ) +
  # star for significance
  annotate(
    geom  = "text",
    label = "*",
    color = "black",
    x = 3,
    y = .95,
    size  = 10 
    ) +
  # dotted line that separates the different questionnaires
  geom_vline(
    aes(xintercept = stage(Questionnaire, after_scale = 3.5)),
    linetype = 3
  ) +
  # star for significance
  annotate(
    geom  = "text",
    label = "*",
    color = "black",
    x = 4,
    y = .95,
    # vjust = .1,
    # hjust = 6,
    size  = 10 
    ) 
```

## Congruence effects

### Correlations

```{r}
#| fig-width: 10
#| fig-height: 6

corr_whole <- 
  df_questionnaires |> 
    select(4:10) |>
    mutate(across(VVIQ:SUIS, rank)) |> 
    correlation(p_adjust = "none")

corr_aph <-
  df_questionnaires |> 
    select(4:10) |>
    filter(aphantasia == "yes") |>
    mutate(across(VVIQ:SUIS, rank)) |> 
    correlation(p_adjust = "none")

corr_control <-
  df_questionnaires |> 
    select(4:10) |>
    filter(aphantasia == "no") |> 
    mutate(across(VVIQ:SUIS, rank)) |> 
    correlation(p_adjust = "none")

corr_whole
corr_aph
corr_control

corr_whole |> summary() |> plot() + 
  labs(title = "Correlation matrix, whole group")

corr_aph |> summary() |> plot() +
  labs(title = "Correlation matrix, aphantasia group only")

corr_control |> summary() |> plot() +
  labs(title = "Correlation matrix, control group only")
```

### Plots

```{r}
#| fig-width: 10
#| fig-height: 6

df_questionnaires |> plot_correlations("VVIQ", "Implicit effect")
df_questionnaires |> plot_correlations("OSIQ_Object", "Implicit effect")
df_questionnaires |> plot_correlations("SUIS", "Implicit effect")
df_questionnaires |> plot_correlations("SUIS", "Explicit effect")

# Ranked versions
df_q_ranked |> plot_correlations("VVIQ", "Implicit effect")
df_q_ranked |> plot_correlations("OSIQ_Object", "Implicit effect")
df_q_ranked |> plot_correlations("SUIS", "Implicit effect")
df_q_ranked |> plot_correlations("SUIS", "Explicit effect")
```

@@

# ggsave(here("figures/checks-implicit.png"), dpi = 600)
```

@@

# ggsave(here("figures/checks-explicit.png"), dpi = 600)
```
